---
title: "Facciabene SBRT patients - taxonomic analysis"
author: "Ceylan Tanes"
date: \today
output: 
  pdf_document:
    toc: true
    toc_depth: 3
---

```{r knitr setup, echo=FALSE, message=FALSE}
library(knitr)
opts_chunk$set(
  tidy=FALSE,
  cache=FALSE,
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  dpi=100,
  fig.width=5,
  fig.height=3,
  fig.align = "center"
  )
```

```{r child = 'facciabene_sbrt_preamble.Rmd'}
```



# SBRT analysis

```{r}
## Subset the metadata file to only keep the samples you would like to test on
s_toTest <- s %>%
  filter(Keep) %>%
  filter(!isControl) %>%
  mutate(study_group_label = fct_relabel(study_group, function(x) sub(" ", "\n", x))) %>%
  droplevels()

## Set colors for each factor ahead of time so they are consistent through the report.
ann_colors = list(
  current_antibiotics = factor_palette(s_toTest$current_antibiotics, as.character(wes_palette("Cavalcanti1"))),
  #sample_type = factor_palette(s_toTest$sample_type, brewer.pal(12, "Paired")),
  study_group = factor_palette(s_toTest$study_group, viridis(5, end=0.8)),
  study_group_label = factor_palette(s_toTest$study_group_label, viridis(5, end=0.8)),
  #study_day = factor_palette(s_toTest$study_day, viridis(length(unique(s_toTest$study_day))) )
  treatment = factor_palette(s_toTest$treatment, as.character(wes_palette("Royal1")))
)

## Change this to be the breakdown of whatever variable the collaborator is interested in
addmargins(table(s_toTest$subject_id, s_toTest$study_group, useNA = "ifany")) %>%
  pander(split.table=Inf)

table(s_toTest$subject_id, s_toTest$treatment)
```


## Taxonomic heatmap

```{r}
prop_cut <- 0.01
```

Taxonomic assignments were performed using the Kraken program.

Heatmap charts were generated from the taxonomic assignments. Each column represents one sample and each row represents one taxon (typically a species). Ranks are included in the plot if the taxon is present in `r 100*prop_cut`% mean abundance in at least one sample type.

The chart is colored white if species were not observed in the sample, dark blue if species were observed at very low abundance.  This allows the reader to quickly survey species presence/absence.  Abundance values exceeding 40% are colored red, indicating an extremely dominant species.


```{r fig.width=20, fig.height=10}
s_toPlot <- s_toTest %>%
  select(SampleID, subject_id, study_group, current_antibiotics, run, treatment) %>%
  arrange(treatment, subject_id, study_group) %>%
  droplevels()

# select taxa with mean relative abundance of 1% in at least one sample type
select_taxa <- summed_props %>%
  as.data.frame() %>% 
  rownames_to_column("Taxa") %>% 
  pivot_longer(-Taxa, names_to="SampleID", values_to="props") %>%
  right_join(s_toPlot, by="SampleID")  %>%
  group_by(Taxa) %>%
  mutate(mean_prop = mean(props)) %>%
  ungroup() %>%
  filter(mean_prop > prop_cut) %>%
  pull(Taxa) %>%
  as.character() %>%
  unique()

props_toPlot <- summed_props[select_taxa, s_toPlot$SampleID]
props_toPlot %>%
  pheat() %>%
  pheat_color_saturated() %>%
  pheat_cluster_rows() %>%
  pheat_annotate_cols(s_toPlot) %>%
  pheat_display_cols(gaps = factor_gaps(s_toPlot$subject_id)) %>%
  pheat_annotation_color(
    current_antibiotics = ann_colors$current_antibiotics,
    study_group = ann_colors$study_group,
    treatment = ann_colors$treatment
  )
```




## Differential abundance


Figure shows all the bacteria that have a mean relative abundance of >1% across samples. Only these bacteria have been tested in this report.

```{r}
props_toTest <- summed_props %>%
  as.data.frame() %>% 
  rownames_to_column("Taxa") %>% 
  pivot_longer(-Taxa, names_to="SampleID", values_to="props") %>%
  right_join(s_toTest, by="SampleID")  %>%
  group_by(Taxa) %>%
  mutate(perc_present = mean(props > 0)) %>%
  mutate(mean_prop = mean(props)) %>%
  ungroup() %>%
  filter(mean_prop > 0.01) %>%
  #filter(mean_prop > 0.01 | Taxa %in% c("Firmicutes Clostridioides difficile", "Firmicutes Enterococcus faecalis")) %>%
  filter(Taxa != "Bacteria") %>%
  
  # take out anything that's not species level
  filter(!Taxa %in% c("Bacteroidetes Bacteroidales", "Bacteroidetes Bacteroides", "Firmicutes Clostridiales","Proteobacteria Enterobacteriaceae")) %>%
  
  mutate(props_original = props) %>%
  mutate(props = props + min(filter(., props>0)$props) / 10) %>%
  mutate(props_log = log10(props))
```



```{r fig.height=18, fig.width=10}
props_toTest %>%
  
  mutate(Taxa = reorder(Taxa, -props)) %>%
  mutate(Taxa = fct_relabel(Taxa, function(x) gsub(" ", "\n", x))) %>%
  
  ggplot(aes(x=study_group_label, y=props, color=study_group_label, shape=current_antibiotics)) +
    geom_boxplot(outlier.alpha=0) +
    geom_line(aes(group=subject_id), color="gray") +
    geom_point() +
    facet_wrap(~Taxa, scales="free", ncol = 4) +
    scale_color_manual(values=ann_colors$study_group_label) +
    scale_shape_manual(values=c(16,1)) +
    scale_y_continuous(labels=scales:::percent) +
    theme_clean() +
    theme(
      axis.text.x=element_text(angle=90, hjust=1, vjust=0.5),
      legend.position = "bottom"
    ) +
    #guides(color="none") +
    labs(
      y="Relative abundance"
    )
```


Linear models were used to estimate the change in relative abundance of select taxa between study groups. The relative abundances were log10 transformed. Multiple tests were adjusted for false discovery rate using Benjamini-Hochberg method. Only the terms with p<0.05 are shown in the table below.

For each time point: props_log ~ treatment

```{r}
summaries_df <- props_toTest %>%
  
  group_by(Taxa, study_group) %>%
  do(tidy(lm(props_log ~ treatment, data=.))) %>%
  ungroup() %>%
  
  filter(!grepl("Intercept|Residuals", term)) %>%
  mutate(term = sub("treatment", "Control - ", term)) %>% 
  
  group_by(term) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup()

summaries_df %>%
  filter(p.value < 0.05) %>%
  kable_style(fdr, 0.05)
```



```{r fig.width=10, fig.height=10}
summaries_df %>%
  
  group_by(Taxa) %>%
  mutate(num_sig = any(fdr<0.05)) %>%
  ungroup() %>%
  filter(num_sig) %>%
  
  separate(Taxa, into=c("Phylum", "Taxa"), extra="merge") %>%
  
  mutate(Taxa = reorder(Taxa, estimate)) %>%
  mutate(isSig = ifelse(fdr < 0.05, "q<0.05", "q>0.05")) %>%
  
  ggplot(aes(x=estimate, y=Taxa, color=study_group, shape=isSig)) +
    geom_vline(xintercept=0, linetype=2) +
    geom_pointrange(aes(xmin=estimate-std.error, xmax=estimate+std.error), position = position_dodge(width = 0.5)) +
    scale_color_manual(values=ann_colors$study_group) +
    scale_shape_manual(values=c(16,1)) +
    facet_grid(Phylum~., space="free", scales="free") +
    theme_clean() +
    theme(
      strip.text.y = element_text(angle = 0)
    ) +
    labs(
      x="Estimated log difference between groups",
      y="", color="", shape=""
    )
```

```{r fig.width=10, fig.height=10}
taxa_toPlot <- summaries_df %>%
  group_by(Taxa) %>%
  mutate(num_sig = any(fdr<0.05)) %>%
  ungroup() %>%
  filter(num_sig) %>%
  select(Taxa, study_group, estimate, fdr)

props_toTest %>%
  right_join(taxa_toPlot, by=c("Taxa", "study_group")) %>%
  
  mutate(significance = case_when(
    fdr < 0.001 ~ "***",
    fdr < 0.01 ~ "**",
    fdr < 0.05 ~ "*"
  )) %>%
  mutate(significance = ifelse(treatment == "control", NA, significance)) %>%
  
  group_by(Taxa) %>%
  mutate(clr_trans = log(props) - mean(log(props))) %>%
  ungroup() %>%
  
  group_by(Taxa, study_group, treatment, significance) %>%
  summarize(props = mean(clr_trans)) %>%
  ungroup() %>%
  
  mutate(study_group = fct_relabel(study_group, function(x) sub(" ", "\n", x))) %>%
  mutate(treatment = stringr::str_to_title(treatment)) %>%
  
  mutate(sig_color = ifelse(abs(props) > 4, "A", "B")) %>%
  
  ggplot(aes(x=treatment, y=Taxa)) +
    geom_tile(aes(fill=props)) +
    geom_text(aes(label=significance, color=sig_color), size=5) +
    scale_fill_gradient2(low="#365C8D", mid="#F7F7F7", high="#1FA187", midpoint=0) +
    scale_color_manual(values=c("#D3D3D3", "#000000")) +
    scale_x_discrete(expand=c(0,0)) +
    scale_y_discrete(expand=c(0,0)) +
    facet_grid(.~study_group, space="free", scales="free") +
    theme_clean() +
    theme(
      strip.text.y = element_text(angle=0),
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)
    ) +
    guides(color="none") +
    labs(
      x="", y="", fill="Mean\nclr\ntransformed\nabundances"
    )
ggsave("facciabene_SBRT_paper_Fig_diffAb.pdf", height=5, width=7.3, useDingbats=F)
```


## Differential abundance: Genus level


Figure shows all the bacteria that have a mean relative abundance of >1% across samples. Only these bacteria have been tested in this report.

```{r}
props_toTest <- summed_props_g %>%
  as.data.frame() %>% 
  rownames_to_column("Taxa") %>% 
  pivot_longer(-Taxa, names_to="SampleID", values_to="props") %>%
  right_join(s_toTest, by="SampleID")  %>%
  group_by(Taxa) %>%
  mutate(perc_present = mean(props > 0)) %>%
  mutate(mean_prop = mean(props)) %>%
  ungroup() %>%
  filter(mean_prop > 0.01 | Taxa %in% c("Firmicutes Enterococcus", "Firmicutes Megasphaera", "Firmicutes Veillonella")) %>%
  filter(Taxa != "Bacteria") %>%
  
  # take out anything that's not species level
  filter(!Taxa %in% c("Firmicutes ", "Bacteroidetes Bacteroidales", "Proteobacteria Enterobacteriaceae")) %>%
  
  mutate(props_original = props) %>%
  mutate(props = props + min(filter(., props>0)$props) / 10) %>%
  mutate(props_log = log10(props))
```



```{r fig.height=18, fig.width=10}
props_toTest %>%
  
  mutate(Taxa = reorder(Taxa, -props)) %>%
  mutate(Taxa = fct_relabel(Taxa, function(x) gsub(" ", "\n", x))) %>%
  
  ggplot(aes(x=study_group_label, y=props, color=study_group_label, shape=current_antibiotics)) +
    geom_boxplot(outlier.alpha=0) +
    geom_line(aes(group=subject_id), color="gray") +
    geom_point() +
    facet_wrap(~Taxa, scales="free", ncol = 4) +
    scale_color_manual(values=ann_colors$study_group_label) +
    scale_shape_manual(values=c(16,1)) +
    scale_y_continuous(labels=scales:::percent) +
    theme_clean() +
    theme(
      axis.text.x=element_text(angle=90, hjust=1, vjust=0.5),
      legend.position = "bottom"
    ) +
    #guides(color="none") +
    labs(
      y="Relative abundance"
    )
```


Linear models were used to estimate the change in relative abundance of select taxa between study groups. The relative abundances were log10 transformed. Multiple tests were adjusted for false discovery rate using Benjamini-Hochberg method. Only the terms with p<0.05 are shown in the table below.


For each time point: props_log ~ treatment

```{r}
summaries_df <- props_toTest %>%
  
  group_by(Taxa, study_group) %>%
  do(tidy(lm(props_log ~ treatment, data=.))) %>%
  ungroup() %>%
  
  filter(!grepl("Intercept|Residuals", term)) %>%
  mutate(term = sub("treatment", "Control - ", term)) %>% ### You only need this when you are not using the tidy_lm_posthoc function
  
  group_by(term) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup()

summaries_df %>%
  filter(p.value < 0.05) %>%
  kable_style(fdr, 0.05) 
```



```{r fig.width=10, fig.height=5}
summaries_df %>%
  
  group_by(Taxa) %>%
  mutate(num_sig = any(fdr<0.05)) %>%
  ungroup() %>%
  filter(num_sig) %>%
  
  separate(Taxa, into=c("Phylum", "Taxa"), extra="merge") %>%
  
  mutate(Taxa = reorder(Taxa, estimate)) %>%
  mutate(isSig = ifelse(fdr < 0.05, "q<0.05", "q>0.05")) %>%
  
  ggplot(aes(x=estimate, y=Taxa, color=study_group, shape=isSig)) +
    geom_vline(xintercept=0, linetype=2) +
    geom_pointrange(aes(xmin=estimate-std.error, xmax=estimate+std.error), position = position_dodge(width = 0.5)) +
    scale_color_manual(values=ann_colors$study_group) +
    scale_shape_manual(values=c(16,1)) +
    facet_grid(Phylum~., space="free", scales="free") +
    #facet_wrap(~sample_type) +
    theme_clean() +
    theme(
      strip.text.y = element_text(angle = 0)
    ) +
    labs(
      x="Estimated log difference between groups",
      y="", color="", shape=""
    )

```


```{r fig.height=6, fig.width=6}
props_toTest %>%
  filter(grepl("Akkermansia|Veillonella|Enterococcus|Megasp", Taxa)) %>%
  
  ggplot(aes(x=study_group_label, y=props, color=study_group_label, shape=treatment)) +
    geom_boxplot(outlier.alpha=0) +
    geom_quasirandom(dodge.width = 0.75) +
    facet_wrap(~Taxa, ncol = 2, scales="free_y") +
    scale_color_manual(values=ann_colors$study_group_label) +
    scale_shape_manual(values=c(16,1)) +
    scale_y_continuous(labels=scales:::percent, trans="log10") +
    theme_clean() +
    theme(
      axis.text.x=element_text(angle=90, hjust=1, vjust=0.5),
      legend.position = "bottom"
    ) +
    guides(color="none") +
    labs(
      x="", shape="",
      y="Relative abundance"
    )
ggsave("facciabene_SBRT_paper_Fig_genus.pdf", height=5, width=5, useDingbats=F)
```

## Differential abundance: Phylum level


Figure shows all the bacteria that have a mean relative abundance of >1% across samples. Only these bacteria have been tested in this report.

```{r}
props_toTest <- summed_props_p %>%
  as.data.frame() %>% 
  rownames_to_column("Taxa") %>% 
  pivot_longer(-Taxa, names_to="SampleID", values_to="props") %>%
  right_join(s_toTest, by="SampleID")  %>%
  group_by(Taxa) %>%
  mutate(perc_present = mean(props > 0)) %>%
  mutate(mean_prop = mean(props)) %>%
  ungroup() %>%
  filter(mean_prop > 0.05) %>%
  filter(Taxa != "Bacteria") %>%
  
  mutate(props_original = props) %>%
  mutate(props = props + min(filter(., props>0)$props) / 10) %>%
  mutate(props_log = log10(props))
```


```{r fig.height=6, fig.width=6}
props_toTest %>%
  mutate(Taxa = sub("Bacteria ", "", Taxa)) %>%
  
  ggplot(aes(x=study_group_label, y=props, color=study_group_label, shape=treatment)) +
    geom_boxplot(outlier.alpha=0) +
    geom_quasirandom(dodge.width = 0.75) +
    facet_wrap(~Taxa, ncol = 2) +
    scale_color_manual(values=ann_colors$study_group_label) +
    scale_shape_manual(values=c(16,1)) +
    scale_y_continuous(labels=scales:::percent, breaks=c(0,0.25,0.5,0.75,1), limits=c(0,1.1)) +
    theme_clean() +
    theme(
      axis.text.x=element_text(angle=90, hjust=1, vjust=0.5),
      legend.position = "bottom"
    ) +
    guides(color="none") +
    labs(
      x="", shape="",
      y="Relative abundance"
    )
ggsave("facciabene_SBRT_paper_Fig_phylum.pdf", height=5, width=5, useDingbats=F)
```


For each time point: props_log ~ treatment

```{r}
summaries_df <- props_toTest %>%
  
  group_by(Taxa, study_group) %>%
  do(tidy(lm(props_log ~ treatment, data=.))) %>%
  ungroup() %>%
  
  filter(!grepl("Intercept|Residuals", term)) %>%
  mutate(term = sub("treatment", "Control - ", term)) %>%
  
  group_by(term, study_group) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup()

summaries_df %>%
  filter(p.value < 0.05) %>%
  kable_style(fdr, 0.05) 
```


For each treatment: props_log ~ study_group

```{r}
summaries_df <- props_toTest %>%
  
  group_by(Taxa, treatment) %>%
  do(tidy(nlme::lme(props_log ~ study_group, random=~1|subject_id, data=., na.action=na.omit), effect="fixed")) %>%
  ungroup() %>%
  
  filter(!grepl("Intercept|Residuals", term)) %>%
  mutate(term = sub("treatment", "Control - ", term)) %>% 
  
  group_by(term, treatment) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup()

summaries_df %>%
  filter(p.value < 0.05) %>%
  kable_style(fdr, 0.05) 
```



```{r}
summaries_df <- props_toTest %>%
  
  group_by(Taxa, treatment) %>%
  do(tidy_lm_posthoc(nlme::lme(props_log ~ study_group, random=~1|subject_id, data=., na.action=na.omit), "study_group")) %>%
  ungroup() %>%
  
  filter(!grepl("Intercept|Residuals", term)) %>%
  mutate(term = sub("treatment", "Control - ", term)) %>%
  
  group_by(term, treatment) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup()

summaries_df %>%
  filter(p.value < 0.05) %>%
  kable_style(fdr, 0.05)
```

## Beta diversity

Here, we use Bray-Curtis and Jaccard distances to compare the species composition of the samples to each other.

The plots below show the distance between each pair of samples in a single 2D plot.  It is not possible to plot the distances exactly on paper, so we have used a method of ordination called Principal Coordinates Analysis to select the best coordinate system for display.  The percentage of total variance captured along each axis is displayed on the chart.


```{r fig.show='hold', out.width='.49\\linewidth', fig.height=3, fig.width=5}
s_toTest %>%
  pcoaplus(bc) %>%
  plot(color=study_group, shape=current_antibiotics) +
    scale_color_manual(values=ann_colors$study_group) +
    scale_shape_manual(values=c(16,1)) +
    theme_clean_pcoa() + 
    labs(color="", title="Bray-Curtis")

s_toTest %>%
  pcoaplus(jd) %>%
  plot(color=study_group, shape=current_antibiotics) +
    scale_color_manual(values=ann_colors$study_group) +
    scale_shape_manual(values=c(16,1)) +
    theme_clean_pcoa() + 
    labs(color="", title="Jaccard")
```

```{r}
s_toTest %>%
  pcoaplus(bc) %>%
  plot(color=study_group, shape=treatment) +
    scale_color_manual(values=ann_colors$study_group) +
    scale_shape_manual(values=c(16,1)) +
    facet_wrap(~study_group, ncol=5) +
    theme_clean_pcoa() +
    guides(color="none") +
    theme(
      legend.position = "bottom"
    ) +
    labs(shape="")
ggsave("facciabene_SBRT_paper_Fig_PCoA_BC.pdf", height=3, width=6, useDingbats=F)
```


```{r}
s_toTest %>%
  filter(study_group %in% c("Start SBRT", "End SBRT")) %>%
  do(adonisplus(
    ., distmat = bc, formula = distmat ~ current_antibiotics + study_group, 
    rep_meas_var=subject_id, shuffle=c(current_antibiotics = "between", study_group = "within"),
    sample_id_var = SampleID, permutations=999)) %>%
  filter(!term %in% c("Residual", "Total")) %>%
  select(-sumsq) %>%
  
  mutate(fdr = p.adjust(p.value, method="BH"))
```

PERMANOVA test on Bray-Curtis and Jaccard distances to test if the centroids of the study groups can be distinguished from each other.

For each study day: distmat ~ treatment

```{r eval=T}
summaries_df <- rbind(
  s_toTest %>%
    group_by(study_group) %>%
    do(adonisplus(
      ., distmat = bc, formula = distmat ~ treatment,
      sample_id_var = SampleID, permutations=999)) %>%
    ungroup() %>%
    mutate(metric = "Bray-Curtis"),
  
  s_toTest %>%
    group_by(study_group) %>%
    do(adonisplus(
      ., distmat = jd, formula = distmat ~ treatment,
      sample_id_var = SampleID, permutations=perm)) %>%
    ungroup() %>%
    mutate(metric = "Jaccard")
) %>%
  filter(!term %in% c("Residual", "Total")) %>%
  select(-sumsq) %>%
  select(metric, everything()) %>%
  
  group_by(metric) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup()

summaries_df %>%
  kable_style()
```


For each treatment: distmat ~ study_day

```{r eval=T}
summaries_df <- rbind(
  s_toTest %>%
    group_by(treatment) %>%
    do(adonispost(
      ., distmat = bc, formula = distmat ~ study_group,
      sample_id_var = SampleID, permutations=999, which = study_group, alpha = 1)) %>%
    ungroup() %>%
    mutate(metric = "Bray-Curtis"),
  
  s_toTest %>%
    group_by(treatment) %>%
    do(adonispost(
      ., distmat = jd, formula = distmat ~ study_group,
      sample_id_var = SampleID, permutations=perm, which = study_group, alpha = 1)) %>%
    ungroup() %>%
    mutate(metric = "Jaccard")
) %>%
  filter(!term %in% c("Residual", "Total")) %>%
  select(-sumsq) %>%
  select(metric, everything()) %>%
  
  group_by(metric, treatment) %>%
  mutate(fdr = p.adjust(p.value, method="BH")) %>%
  ungroup()

summaries_df %>%
  kable_style()
```

## Alpha diversity

Alpha diversity was assessed by the expected number of observed OTUs (out of rarefying sample size of `r format(richness_subsample_size, big.mark = ",", scientific = F)`) and Shannon index.

```{r fig.width=8}
s_toTest %>%
  pivot_longer(c("Richness", "Shannon"), names_to="metric", values_to="alpha") %>%

  ggplot(aes(x=study_group, y=alpha, color=study_group, shape=current_antibiotics)) +
    geom_boxplot(outlier.alpha=0) +
    geom_quasirandom(dodge.width=0.75) +
    facet_grid(metric~., scales = "free") +
    scale_color_manual(values=ann_colors$study_group) +
    scale_shape_manual(values=c(16,1)) +
    theme_clean() +
    #guides(color="none") +
    labs(
      x="", color="",
      y="Alpha diversity value"
    )
```


```{r}
s_toTest %>%

  ggplot(aes(x=study_group_label, y=Shannon, color=study_group_label, shape=treatment)) +
    geom_boxplot(outlier.alpha=0) +
    geom_quasirandom(dodge.width=0.75) +
    scale_color_manual(values=ann_colors$study_group_label) +
    scale_shape_manual(values=c(16,1)) +
    scale_y_continuous(limits=c(1.5, 5.7)) +
    theme_clean() +
    guides(color="none") +
    theme(
      #aspect.ratio = 0.5
      legend.position = "bottom"
    ) +
    labs(
      x="", color="", shape="",
      y="Shannon diversity"
    )
ggsave("facciabene_SBRT_paper_Fig_alpha.pdf", height=3, width=5, useDingbats=F)
```


Linear models were used to estimate the difference between study groups.


For each study day: alpha ~ treatment

```{r}
summaries_df <- s_toTest %>%
  pivot_longer(c("Richness", "Shannon"), names_to="metric", values_to="alpha") %>%
  
  group_by(metric, study_group) %>%
  do(tidy(lm(alpha ~ treatment, data=.))) %>%
  ungroup() %>%
  
  filter(!grepl("Intercept|Residuals", term)) %>%
  mutate(term = sub("treatment", "Control - ", term))

summaries_df %>%
  kable_style()
```


For each treatment group: alpha ~ study_group, random=~1|subject_id

```{r}
summaries_df <- s_toTest %>%
  pivot_longer(c("Richness", "Shannon"), names_to="metric", values_to="alpha") %>%
  
  group_by(metric, treatment) %>%
  do(tidy_lm_posthoc(nlme::lme(alpha ~ study_group, random=~1|subject_id, data=., na.action=na.omit), "study_group")) %>%
  ungroup() %>%
  
  filter(!grepl("Intercept|Residuals", term))

summaries_df %>%
  kable_style()
```


